Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Polished "Markup for examples"

\noindent First, we introduce new Haddock markup for interactive examples.
In this paper, we use {\tt >>>} which is the same as Python's one.
Here is an example:

@@

\noindent The first line starts with {\tt >>>} and an expression follows. The second line contains its result. We can write this by copy-and-pasting from an interpreter and modifying the prompt.
It's worth explaining that we can specify operation sequences:

@@

\noindent Also, we can show exceptions.

>>>>

We introduce new Haddock markup for interactive examples.  A line
starting with a \emph{prompt} (``{\tt >>>}'') denotes an expression.
Lines following an expression denote the result of that expression.
Here is an example:

@@

\noindent The result ends at the next empty line, or another prompt.
It is possible to specify example sequences:

@@

\noindent Result is defined by what GHCi prints to stdout and stderr
when evaluating the expression.  This, e.g. also allows to document
exceptions:
